### 2019-11-09 boek.tex
technical fixes

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} A common problem of pioneering computational tools is that during their development, there are rarely sufficient datasets available for adequately quantitatively assessing its performance. \\
	\textbf{Results:} We developed \texttt{dyngen}, a multi-modality simulator of single cells. 
	In dyngen, the biomolecular state of an \textit{in silico} cell changes over time according to a set of reactions defined by the cell's gene regulatory network. By simulating single cells in terms of its biomolecular state and reactions, the simulator is easily extendible for adding new modalities or experimental procedures. We demonstrate \texttt{dyngen}'s flexibility by simulating snapshot, time-series and perturbation experiments.\\
	\textbf{Conclusion:} \texttt{dyngen} lays the foundations for benchmarking a wide variety of computational single-cell tools, and can be used to help kick-start the development of future types of analyses.
\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   CH9: Self-assessment    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 7: Self-assessment in trajectory inference} 
\chaptermark{Paper 7: Self-assessment in trajectory inference.} % short title
\label{chap:selfassessment}

@@

\ifrenderall
\newpage
\graphicspath{{./ch9_selfassessment/}}
\include{ch9_selfassessment/content}
\clearpage
\section{References}
\printbibliography[heading=none]
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH10: Guidelines    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 8: Essential guidelines for computational method benchmarking} 
\chaptermark{Paper 8: Essential guidelines for computational method benchmarking.} % short title
\label{chap:guidelines}

@@

\ifrenderall
\newpage
\graphicspath{{./ch10_guidelines/}}
\include{ch10_guidelines/content}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%      CH8: DISCUSSION      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Discussion} 
\chaptermark{Discussion.} % short title
\label{chap:discussion}

\ifrenderall
\newpage
\graphicspath{{./ch8_discussion/}}
\include{ch8_discussion/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        BACKMATTER         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chX_backmatter}

>>>>

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} A common problem of pioneering computational tools is that during their development, there are rarely sufficient datasets available for adequately quantitatively assessing its performance. \\
	\textbf{Results:} We developed \texttt{dyngen}, a multi-modality simulator of single cells. 
	In \texttt{dyngen}, the biomolecular state of an \textit{in silico} cell changes over time according to a set of reactions defined by the cell's gene regulatory network. By simulating single cells in terms of its biomolecular state and reactions, the simulator is easily extendible for adding new modalities or experimental procedures. We demonstrate \texttt{dyngen}'s flexibility by simulating snapshot, time-series and perturbation experiments.\\
	\textbf{Conclusion:} \texttt{dyngen} lays the foundations for benchmarking a wide variety of computational single-cell tools, and can be used to help kick-start the development of future types of analyses.
\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   CH8: Self-assessment    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 7: Self-assessment in trajectory inference} 
\chaptermark{Paper 7: Self-assessment in trajectory inference.} % short title
\label{chap:selfassessment}

@@

\ifrenderall
\newpage
\graphicspath{{./ch8_selfassessment/}}
\include{ch8_selfassessment/content}
\clearpage
\section{References}
\printbibliography[heading=none]
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH9: Guidelines    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 8: Essential guidelines for computational method benchmarking} 
\chaptermark{Paper 8: Essential guidelines for computational method benchmarking.} % short title
\label{chap:guidelines}

@@

\ifrenderall
\newpage
\graphicspath{{./ch9_guidelines/}}
\include{ch9_guidelines/content}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%      CH10: DISCUSSION      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Discussion} 
\chaptermark{Discussion.} % short title
\label{chap:discussion}

\ifrenderall
\newpage
\graphicspath{{./ch10_discussion/}}
\include{ch10_discussion/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        BACKMATTER         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chX_backmatter}

### 2019-11-09 ch7_incgraph/content.tex
technical fixes

%% FIGURE 6
\picfig{fig/figure6.pdf}{\Largefigure}{fig_reranking}{{\bf A simple graphlet-based scoring method improves predicted regulatory networks.}
	(A) The F1 score was calculated by calculating the harmonic mean of the AUROC and AUPR scores of the first 1000 interactions. (B) IncGraph is significantly faster than the non-incremental approach. Note that for each interaction added to the network, the graphlet counts of 100 putative interactions were evaluated.}

>>>>

%% FIGURE 6
\picfig{fig/figure6.png}{\Largefigure}{fig_reranking}{{\bf A simple graphlet-based scoring method improves predicted regulatory networks.}
	(A) The F1 score was calculated by calculating the harmonic mean of the AUROC and AUPR scores of the first 1000 interactions. (B) IncGraph is significantly faster than the non-incremental approach. Note that for each interaction added to the network, the graphlet counts of 100 putative interactions were evaluated.}
